What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2025-01-02 Manuscript files/Manuscript.qmd
Title page and typos
Title page and figures

author:
  - name: "Thomas Reiter"
    affiliations: [stat-consulting]
  - name: "Philipp Sterner"
    affiliations: [stat-consulting]

affiliations:
  - id: stat-consulting
    name: "Statistical Consulting, Master Statistics and Data Science, LMU Munich, Institute of Statistics"

abstract: |
  **Supervisor:** Prof. Dr. David Rügamer

  **Project Partners:** Prof. Dr. Paul Thurner and Fabian Haggerty  
  (Geschwister Scholl Institute of Political Science)

date: "2024-12-20"

@@

All analyses including a reproducible can be found at \url{https://github.com/T-Reiter/Statistical_Consulting}.

@@

## A3 Convergence Diagnostic Traceplot - Attribute: Ukrainian Soldiers Killed 
```{r convergence-diagnostics-usk, echo=FALSE, fig.align='center', fig.fullwidth=TRUE, out.width="100%"}
#| fig-subcap: "Exemplary Posterior Draw Traceplots for Convergence Assessment - Attribute 1"
#| fig-cap: "Note. Rows 1 and 2 display Traceplots of Draws from the BART Posterior Distribution for the selection probabilities (p_hat_0 and p_hat_1) if Attribute 1 (Ukrainian Military Casualties) was set to the reference level (i.e., 12,500) or first level of interest (i.e., 25,000). Row 3 represents the associated OMCE 'draws' calculcate by taking the different of p_hat_1 and p_hat_0. Columns 1 and 2 contain draws from the default sized BART model (Burn-In: 100, Posterior Draws: 1000) and larger BART Models (Burn-In: 1000, Posterior Draws: 5000)\\linebreak Models were fit using parallel computation on 4 cores."
#| label: convergence-diagnostics-usk
# if needed add linebreaks in fig-cap via \\linebreak

@@

# Single grobs for rows with newline and adjusted lineheight
row_header_combined_1 <- textGrob(paste0("$p^{hat}_{0}$\n",
                                         "phat_0[,1]"), x=0, hjust=0, 
                                  gp=gpar(fontsize=10, lineheight=1))
row_header_combined_2 <- textGrob(paste0("p_hat_1\n",
                                         "phat_0[,1]"), x=0, hjust=0,
                                  gp=gpar(fontsize=10, lineheight=1))
row_header_combined_3 <- textGrob(paste0("omce_1\n",
                                         "omces[,1]"), x=0, hjust=0,
                                  gp=gpar(fontsize=10, lineheight=1))

@@

# Single grobs for rows with newline and adjusted lineheight
row_header_combined_1 <- textGrob(paste0("p_hat_0\n",
                                         "phat_0[,1]"), x=0, hjust=0, 
                                  gp=gpar(fontsize=10, lineheight=1))
row_header_combined_2 <- textGrob(paste0("p_hat_1\n",
                                         "phat_0[,1]"), x=0, hjust=0,
                                  gp=gpar(fontsize=10, lineheight=1))
row_header_combined_3 <- textGrob(paste0("omce_1\n",
                                         "omces[,1]"), x=0, hjust=0,
                                  gp=gpar(fontsize=10, lineheight=1))

@@

# Single grobs for rows with newline and adjusted lineheight
row_header_combined_1 <- textGrob(paste0("p_hat_0\n",
                                         "reference\nlevel"), x=0, hjust=0, 
                                  gp=gpar(fontsize=10, lineheight=1))
row_header_combined_2 <- textGrob(paste0("p_hat_1\n",
                                         "level of\ninterest"), x=0, hjust=0,
                                  gp=gpar(fontsize=10, lineheight=1))
row_header_combined_3 <- textGrob(paste0("omce_1\n",
                                         "OMCE"), x=0, hjust=0,
                                  gp=gpar(fontsize=10, lineheight=1))

>>>>

author:
  - name: | 
          | Thomas Reiter
          | t.reiter@psy.lmu.de

  - name: | 
          | Philipp Sterner
          | p.sterner@psy.lmu.de

  - name: |
          | Statistical Consulting
          | Master Statistics and Data Science
          | LMU Munich, Institute of Statistics

abstract: |
  | **Supervisor:** 
  | Prof. Dr. David Rügamer

  | **Project Partners:** 
  | Prof. Dr. Paul Thurner and Fabian Haggerty 
  | (Geschwister Scholl Institute of Political Science)

  | **Date:** 
  | Munich, January 2, 2024

@@

The code to reproduce the analyses can be found at \url{https://github.com/T-Reiter/Statistical_Consulting}.

@@

## A3 Convergence Diagnostic Traceplot - Attribute: Ukrainian Soldiers Killed 
```{r convergence-diagnostics-usk, echo=FALSE, fig.align='center', fig.fullwidth=TRUE, out.width="100%"}
#| fig-subcap: "Exemplary Posterior Draw Traceplots for Convergence Assessment - Attribute 1"
#| fig-cap: "Note. Rows 1 and 2 display Traceplots of Draws from the BART Posterior Distribution for the selection probabilities (p_hat_0 and p_hat_1) if Attribute 1 (Ukrainian Military Casualties) was set to the reference level (i.e., 12,500) or first level of interest (i.e., 25,000). Row 3 represents the associated OMCE 'draws' calculcate by taking the different of p_hat_1 and p_hat_0. Columns 1 and 2 contain draws from the default sized BART model (Burn-In: 100, Posterior Draws: 1000) and larger BART Models (Burn-In: 1000, Posterior Draws: 5000)\\linebreak Models were fit using parallel computation on 4 cores."
#| label: convergence-diagnostics-usk

@@

# Single grobs for rows (using expressions for hats)
row_header_combined_1 <- textGrob(
  expression(paste(hat(p)[0], "[,1]")),
  x=0, hjust=0, 
  gp=gpar(fontsize=10, lineheight=1)
)
row_header_combined_2 <- textGrob(
  expression(paste(hat(p)[1], "[,1]")),
  x=0, hjust=0,
  gp=gpar(fontsize=10, lineheight=1)
)
row_header_combined_3 <- textGrob(
  paste0("omces[,1]"), 
  x=0, hjust=0,
  gp=gpar(fontsize=10, lineheight=1)
)

@@

# Single grobs for rows with newline and adjusted lineheight
row_header_combined_1 <- textGrob(
  expression(paste(hat(p)[0], "[,1]")),
  x=0, hjust=0, 
  gp=gpar(fontsize=10, lineheight=1)
)
row_header_combined_2 <- textGrob(
  expression(paste(hat(p)[1], "[,1]")),
  x=0, hjust=0,
  gp=gpar(fontsize=10, lineheight=1)
)
row_header_combined_3 <- textGrob(
  paste0("omces[,1]"), 
  x=0, hjust=0,
  gp=gpar(fontsize=10, lineheight=1)
)

@@

# Single grobs for rows with newline and adjusted lineheight
row_header_combined_1 <- textGrob(
  expression(
    atop(
      paste(hat(p)[0], "[,1]"),
      "reference"
    )
  ),
  x = 0, hjust = 0,
  gp = gpar(fontsize = 10, lineheight = 1)
)
row_header_combined_2 <- textGrob(
  expression(
    atop(
      paste(hat(p)[1], "[,1]"),
      "interest"
    )
  ),
  x = 0, hjust = 0,
  gp = gpar(fontsize = 10, lineheight = 1)
)
row_header_combined_3 <- textGrob(
  expression(
    atop(
      paste("omces[,1]"),
      "OMCE"
    )
  ),
  x = 0, hjust = 0,
  gp = gpar(fontsize = 10, lineheight = 1)
)
